CRUSE to Safe Cycling in Ireland

### 2023-10-07 paper.qmd
More acknowledgements

Transport is responsible for 23% of global greenhouse gas emissions, 70% of which are from road transport.
Nearly nearly half of these emissions (around 10% of global emissions) are from passenger cars [@jaramillo2022].
The transport system encourages, enables and in some cases enforces unsustainable lifestyles.
Services that are only accessible by car lock-in car dependency [@gray2001; @shergold2012; @motte-baumvol2010].

@@

Uptake of cycling should be seen in this broader context of transport decarbonisation [@brand2020] and sustainable mobility [@burns2013].
Although cycling uptake appears on the surface to only relate to the 'shift' part of the ASI framework, closer consideration of the knock-on impacts of cycling uptake shows that it can also help avoid unnecessary trips [@nello-deakin2020].
Furthermore, highly efficient e-bikes --- which are seeing rapid uptake in Ireland and other countries --- outperform electric cars, which are too heavy and expensive.
Over-reliance on electric cars could slow the transition away from car dependency and inadvertently enable "high travel lock-in" [@anable2019].
At the European level, the European Union has a target of reducing greenhouse gas emissions by 55% by 2030, compared to 1990 levels, and to achieve 'net-zero' by 2050.[^1]

@@

The Climate Action Plan scenario is loosely based on the Irish Government's [Climate Action Plan 2021](https://www.gov.ie/en/publication/6223e-climate-action-plan-2021/), which contains policies for action to achieve a 51% reduction in overall greenhouse gas emissions by 2030, on a path towards net-zero by 2050.
For transport, this includes 500,000 extra walking, cycling and public transport trips per day by 2030.
In terms of car travel, the target is to "Increas\[e\] the proportion of kilometres driven by passenger electric cars to between 40 and 45% by 2030, in addition to a reduction of 10% in kilometres driven by the remaining internal combustion engine cars." This equates to a 5.5 to 6% reduction in total car km driven.

@@

@@

Thanks to Paul MacDonald and Donal Hodgins (Kildare County Council), for testing early versions of the tool and for their input into the project.
Thanks to Ciaran Maguire, Catherine Swift, and others at AECOM for their input into the project.

>>>>

Transport is responsible for 23% of global greenhouse gas (GHG) emissions, 70% of which are from road transport.
Nearly nearly half of these emissions (around 10% of global emissions) are from passenger cars [@jaramillo2022].
The transport system encourages, enables and in some cases enforces unsustainable lifestyles.
Services that are only accessible by car lock-in car dependency [@gray2001; @shergold2012; @motte-baumvol2010].

@@

Uptake of cycling should be seen in this broader context of transport decarbonisation [@brand2020] and sustainable mobility [@burns2013].
Although cycling uptake appears on the surface to only relate to the 'shift' part of the ASI framework, closer consideration of the knock-on impacts of cycling uptake shows that it can also help avoid unnecessary trips [@nello-deakin2020].
Furthermore, highly efficient e-bikes --- which are seeing rapid uptake in Ireland and other countries --- outperform electric cars, which are too heavy and expensive.
Over-reliance on electric cars could slow the transition away from car dependency and inadvertently enable "high travel lock-in" [@anable2019].
At the European level, the European Union has a target of reducing GHG emissions by 55% by 2030, compared to 1990 levels, and to achieve 'net-zero' by 2050.[^1]

@@

The Climate Action Plan scenario is loosely based on the Irish Government's [Climate Action Plan 2021](https://www.gov.ie/en/publication/6223e-climate-action-plan-2021/), which contains policies for action to achieve a 51% reduction in overall GHG emissions by 2030, on a path towards net-zero by 2050.
For transport, this includes 500,000 extra walking, cycling and public transport trips per day by 2030.
In terms of car travel, the target is to "Increas\[e\] the proportion of kilometres driven by passenger electric cars to between 40 and 45% by 2030, in addition to a reduction of 10% in kilometres driven by the remaining internal combustion engine cars." This equates to a 5.5 to 6% reduction in total car km driven.

@@

GHG: Greehouse Gas

@@

Thanks to Paul MacDonald and Donal Hodgins (Kildare County Council), for testing early versions of the tool and for their input into the project.
Thanks to Ciaran Maguire, Catherine Swift, and others at AECOM for their input into the project.
Thanks to Martin Lucas-Smith and Simon Nutall from CycleStreets for their input into the project.
